A novel distributed nature-inspired algorithm for solving optimization problems\thanks{Supported by TECNOLÓGICO NACIONAL DE MÉXICO (TecNM).}

### 2021-09-29 paper.tex
Work in progress
Sorted bib file

One strategic difference in our algorithm implementation is the reproduction
process, which is flexible to work in parallel with multiple couple selection
methods, for example, tournament selection, random selection (closed
reproduction), and couple match by creating a new mating individual (open
reproduction). We use many combinations of the containerized processes, up to
the minimum number required to obtain good results. Figure~\ref{fig5} shows a comparison
of only two alternatives for the implementation of the algorithm. Our
experimentation started with a configuration of ten processes and ended in
five, shown on the left and right sides of Fig.~\ref{fig5}, respectively.

@@

For each experiment, we ran 60 independent executions per algorithm and
recorded the following results: Last Generation, Total Evaluations, Time
(seconds), Evaluations/second. The labels used on the header of the results of
our summarized experiments tables are the following:

>>>>

One strategic difference in our algorithm implementation is the reproduction
process, which is flexible to work in parallel with multiple couple selection
methods, for example, tournament selection, random selection (Closed
Reproduction process), and couple match by creating a new mating individual
(Open Reproduction process). We use many combinations of the containerized
processes, up to the minimum number required to obtain good results.
Figure~\ref{fig5} shows a comparison of only two alternatives for the
implementation of the algorithm. Our experimentation started with a
configuration of ten processes and ended in five, shown on the left and right
sides of Fig.~\ref{fig5}, respectively.

@@

For each experiment, we ran 60 independent executions per algorithm and
recorded the following results: Last Generation, Total Evaluations, Time
(seconds), Evaluations/second. The labels used on the results of our summarized
experiments tables are the following:
